---
title: "Aggregating pairs"
author: "Anna Talucci"
date: "2024-09-27"
output: html_document
---

# clear environment
```{r}
rm(list=ls())
```

# Overview
Figures looking at measured versus predicted


# Packages

```{r}
library(tidyverse)
library(lubridate)
library(ggpubr)
library(ggnewscale)
library(ggthemes)
```

# Plot themes
```{r}
comp_theme = theme_bw() + theme(legend.position = "bottom") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"))
```

# Data

## Predicted measurements

```{r}
datacubePred = read_csv("../data/dataCube/PermafrostFireDatacubeFinal.csv")
```

```{r}
datacubePred
```

# Depth difference by biome and permafrost extent

## By Biome

```{r}
( aggregateUnburnedB = datacubePred %>% 
    drop_na(paired) %>%
    filter(distur =="unburned") %>%
  group_by(resBiome, distur, permaExtent, tsf) 
)
```
%>%
  summarise(n = n(),
            mean = mean(predDepth),
            sd   = sd(predDepth, na.rm=TRUE),
            se   = sd / sqrt(n))  %>%
    dplyr::select(resBiome:tsf, mean, se) %>%
  rename(mean_unburned = mean, se_unburned = se, disturUnburn = distur)
```{r}
( aggregateBurnedB = datacubePred %>% 
    drop_na(paired) %>%
    filter(distur =="burned") %>%
  group_by(paired, resBiome, distur, permaExtent, tsfClass) 
)
```
%>%
  summarise(n = n(),
            mean = mean(predDepth),
            sd   = sd(predDepth, na.rm=TRUE),
            se   = sd / sqrt(n))  %>%
    dplyr::select(resBiome:tsfClass, mean, se) %>%
  rename(mean_burned = mean, se_burned = se, disturBurn = distur) 