---
title: "Data for Overview map"
author: "Anna Talucci"
date: "2024-09-13"
output: html_document
---

# clear environment
```{r}
rm(list=ls())
```


# Overview

Create Data layers for overview map.

- Create Map centroids.
-

# Packages

```{r}
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(cowplot)
library(ggpubr)
library(ggnewscale)
```

# Data

## Points

```{r}
datacubePts = st_read("../data/dataCube/PermafrostFireDataCube.shp", "PermafrostFireDataCube")
```

```{r}
datacubePts
```

## Resolve

```{r}
resolve = st_read("../data/spatialData/RESOLVE_Ecoregions_and_Biomes/Biomes_and_Ecoregions_2017.shp", "Biomes_and_Ecoregions_2017")
```

```{r}
resolve
```

## Permafrost

```{r}
permafrost = st_read("../data/spatialData/permafrost/permaice.shp", "permaice")
```

```{r}
permafrost
```

# Reproject

```{r}
permafrost_wgs = st_transform(permafrost, crs= st_crs(datacubePts))
```

```{r}
permafrost_wgs
```

```{r}
unique(permafrost_wgs$NUM_CODE)
unique(permafrost_wgs$COMBO)
unique(permafrost_wgs$RELICT)
unique(permafrost_wgs$EXTENT)
unique(permafrost_wgs$CONTENT)
unique(permafrost_wgs$LANDFORM)
```


# Add Resolve ecozones to points

```{r}
( resTunBor = resolve %>% 
    filter(REALM %in% c("Palearctic", "Nearctic")) %>% 
    dplyr::select(OBJECTID, ECO_NAME, BIOME_NUM, BIOME_NAME, REALM, ECO_ID, geometry) %>% 
    filter(BIOME_NUM %in% c(11, 6)) %>%
    rename(resId = OBJECTID, resName=ECO_NAME, resBiomNm = BIOME_NUM, resBiomeName = BIOME_NAME, resRealm = REALM,  resEcoId = ECO_ID)
)
```

## Join eczones to points

```{r}
points = st_join(datacubePts, resTunBor) 
```

```{r}
points
```



## Add Permafrost extent

```{r}
points_prj = st_transform(points, crs=st_crs(permafrost))
```

```{r}
points_prj
```

```{r}
pt_res_perma = st_join(points_prj, permafrost) 
```

```{r}
( pt_res_perma_Rename = pt_res_perma %>% 
  rename(permaCode = NUM_CODE, permaCombo =COMBO , permaRelict =RELICT , permaExtent= EXTENT, permaCont = CONTENT, permaLand = LANDFORM) )
```

```{r}
permResPt_Wgs = st_transform(pt_res_perma_Rename, crs=4326)
```

```{r}
permResPt_Wgs
```

```{r}
unique(permResPt_Wgs$submitNm)
```

## Save 

```{r eval=FALSE, include=FALSE}
st_write(permResPt_Wgs, "../outputs/spatialDataCreate/PermafrostFireEcozoneDatacube.gpkg")
```

# Resolve Ecozones for Map

## Summaries sites by 

```{r}
(
  resPtCt <- permResPt_Wgs %>% 
    st_drop_geometry() %>%
    group_by(resName) %>%
    summarise(count = n()) %>%
    mutate(total = sum(count)) %>%
  mutate(prop = round(count/total, 5)) %>%
  mutate(percent = round(prop*100, 2)) 
  )
```

```{r}
( ecoCentroidSummary <- permResPt_Wgs %>%
                group_by(resName) %>%
                summarise(st_union(geometry)) %>%
                st_centroid() %>%
  left_join(., resPtCt, by= 'resName') %>%
  mutate(total = sum(count)) %>%
  mutate(prop = round(count/total, 5)) %>%
  mutate(percent = round(prop*100, 2)) %>%
  dplyr::mutate(lon = sf::st_coordinates(.)[,1],
                lat = sf::st_coordinates(.)[,2]) %>%
  st_drop_geometry() %>%
    drop_na(resName) 
  )

```




# Centroid by each region

### 1. "Arctic coastal tundra"

```{r}
res01 =  resTunBor %>% 
    filter(resName=='Arctic coastal tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Arctic coastal tundra')
```

### 2. "Arctic foothills tundra"

```{r}
res02 =  resTunBor %>% 
    filter(resName=='Arctic foothills tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Arctic foothills tundra')
```

### 3. "Beringia lowland tundra"

```{r}
res03 =  resTunBor %>% 
    filter(resName=='Beringia lowland tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Beringia lowland tundra')
```


3              Beringia lowland tundra POINT (-160.8539 60.86536)
4               Beringia upland tundra POINT (-161.7837 62.63477)

### 4. "Beringia upland tundra" 

```{r}
( res04 =  resTunBor %>% 
    filter(resName=='Beringia upland tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Beringia upland tundra') )
```
Longitude: -165.43798
Latitude: 64.52649

### 5. Chukchi Peninsula tundra 

```{r}
res05 =  resTunBor %>% 
    filter(resName=="Chukchi Peninsula tundra") %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName="Chukchi Peninsula tundra")
```

### 6. "East Siberian taiga" 

```{r}
res06 =  resTunBor %>% 
    filter(resName=="East Siberian taiga") %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName="East Siberian taiga")
```


### 7. "Interior Alaska-Yukon lowland taiga"

```{r}
res07 =  resTunBor %>% 
    filter(resName=='Interior Alaska-Yukon lowland taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Interior Alaska-Yukon lowland taiga')
```

### 8. "Interior Yukon-Alaska alpine tundra"

```{r}
res08 =  resTunBor %>% 
    filter(resName=='Interior Yukon-Alaska alpine tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Interior Yukon-Alaska alpine tundra')
```

### 9. "Muskwa-Slave Lake forests"

```{r}
( res09 =  resTunBor %>% 
    filter(resName=='Muskwa-Slave Lake taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Muskwa-Slave Lake taiga') 
  )
```

### 10. "Northeast Siberian taiga"

```{r}
res10=  resTunBor %>% 
    filter(resName=='Northeast Siberian taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Northeast Siberian taiga')
```

### 11. "Northern Canadian Shield taiga"

```{r}
res11=  resTunBor %>% 
    filter(resName=='Northern Canadian Shield taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Northern Canadian Shield taiga')
```

### 12. "Northwest Territories taiga"

```{r}
( res12=  resTunBor %>% 
    filter(resName=='Northwest Territories taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName='Northwest Territories taiga')
)
```

### 13. "Yamal-Gydan tundra"

```{r}
res13 =  resTunBor %>% 
    filter(resName=="Yamal-Gydan tundra") %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(resName="Yamal-Gydan tundra")
```

## Recombine ecoregions

```{r}
( 
  resCentroid = bind_rows(res01, res02, res03, res04, res05, res06, res07, res08, res09, res10, res11, res12, res13) %>% 
    rename(geometry = x)
)
```
 
## Edit geometry of 'Arctic coastal tundra' because of overalp

-142.3674 70.75167
```{r eval=FALSE, include=FALSE}
st_geometry(resCentroid) <- st_sfc(
    ifelse(resCentroid$resName == 'Arctic coastal tundra', st_sfc(st_point(c(-142.3674, 70.75167))), resCentroid$geometry),
    crs = st_crs(resCentroid$geometry))
```

```{r}
resCentroid
```

## Reproject and finalize

### Projection
[Some projection info]https://nsidc.org/data/user-resources/help-center/guide-nsidcs-polar-stereographic-projection)

```{r}
polarProj = "+proj=stere +lat_0=90 +lat_ts=70 +lon_0=-45 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +type=crs"
```

### combine summary percent with centroids

```{r}
( resCentroidreproj = resCentroid %>% 
    st_transform(., crs = polarProj) %>% 
    dplyr::mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>%
  left_join(., resPtCt, by='resName') 
)


```

## Save 

```{r eval=FALSE, include=FALSE}
st_write(resCentroidreproj, "../outputs/spatialDataCreate/EcozoneResCentroids.gpkg")
```



