---
title: "Data for Overview map"
author: "Anna Talucci"
date: "2024-09-13"
output: html_document
---

# clear environment
```{r}
rm(list=ls())
```


# Overview

Create Data layers for overview map.

- Create Map centroids.
-

# Packages

```{r}
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(cowplot)
library(ggpubr)
library(ggnewscale)
```

# Data

## Final datacube

```{r}
dataFinal = read_csv("../data/2025-02-22_PCNFinal/FireAltEstimatedRawData.csv")
```

## Resolve

```{r}
resolve = st_read("../data/spatialData/RESOLVE_Ecoregions_and_Biomes/Biomes_and_Ecoregions_2017.shp", "Biomes_and_Ecoregions_2017")
```

```{r}
resolve
```

## Function to make points
```{r}
df_to_sf <- function(x){
  st_as_sf(x, coords = c("lon","lat"), crs = 4326, remove = FALSE)
}
```

```{r}
pts = dataFinal %>% df_to_sf()
```


# Summaries sites by ecozone

```{r}
(
  resPtCt <- dataFinal %>% 
    group_by(resName) %>%
    summarise(count = n()) %>%
    mutate(total = sum(count)) %>%
  mutate(prop = round(count/total, 5)) %>%
  mutate(percent = round(prop*100, 2)) 
  )
```






# Centroid by each region



### 2. "Arctic foothills tundra"

```{r}
res02 =  resolve%>% 
    filter(ECO_NAME=='Arctic foothills tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Arctic foothills tundra')
```

### 3. "Beringia lowland tundra"

```{r}
res03 =  resolve%>% 
    filter(ECO_NAME=='Beringia lowland tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Beringia lowland tundra')
```


3              Beringia lowland tundra POINT (-160.8539 60.86536)
4               Beringia upland tundra POINT (-161.7837 62.63477)

### 4. "Beringia upland tundra" 

```{r}
( res04 =  resolve%>% 
    filter(ECO_NAME=='Beringia upland tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Beringia upland tundra') )
```
Longitude: -165.43798
Latitude: 64.52649

### 5. Chukchi Peninsula tundra 

```{r}
res05 =  resolve%>% 
    filter(ECO_NAME=="Chukchi Peninsula tundra") %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME="Chukchi Peninsula tundra")
```

### 6. "East Siberian taiga" 

```{r}
res06 =  resolve%>% 
    filter(ECO_NAME=="East Siberian taiga") %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME="East Siberian taiga")
```


### 7. "Interior Alaska-Yukon lowland taiga"

```{r}
res07 =  resolve%>% 
    filter(ECO_NAME=='Interior Alaska-Yukon lowland taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Interior Alaska-Yukon lowland taiga')
```

### 8. "Interior Yukon-Alaska alpine tundra"

```{r}
res08 =  resolve%>% 
    filter(ECO_NAME=='Interior Yukon-Alaska alpine tundra') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Interior Yukon-Alaska alpine tundra')
```

### 9. "Muskwa-Slave Lake forests"

```{r}
( res09 =  resolve%>% 
    filter(ECO_NAME=='Muskwa-Slave Lake taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Muskwa-Slave Lake taiga') 
  )
```

### 10. "Northeast Siberian taiga"

```{r}
res10=  resolve%>% 
    filter(ECO_NAME=='Northeast Siberian taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Northeast Siberian taiga')
```

### 11. "Northern Canadian Shield taiga"

```{r}
res11=  resolve%>% 
    filter(ECO_NAME=='Northern Canadian Shield taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Northern Canadian Shield taiga')
```

### 12. "Northwest Territories taiga"

```{r}
( res12=  resolve%>% 
    filter(ECO_NAME=='Northwest Territories taiga') %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME='Northwest Territories taiga')
)
```

### 13. "Yamal-Gydan tundra"

```{r}
res13 =  resolve%>% 
    filter(ECO_NAME=="Yamal-Gydan tundra") %>%
    st_geometry() %>% # pull just geometry
  st_combine() %>%  # from many points to a single multipoint
  st_centroid() %>% # compute centroid of the multipoint
  st_as_sf() %>% # make it a sf object again 
  mutate(ECO_NAME="Yamal-Gydan tundra")
```

## Recombine ecoregions

```{r}
( 
  resCentroid = bind_rows(res02, res03, res04, res05, res06, res07, res09, res10, res11, res12, res13) %>% 
    rename(geometry = x)
)
```
 


```{r}
resCentroid
```

## Reproject and finalize

### Projection
[Some projection info]https://nsidc.org/data/user-resources/help-center/guide-nsidcs-polar-stereographic-projection)

```{r}
polarProj = "+proj=stere +lat_0=90 +lat_ts=70 +lon_0=-45 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +type=crs"
```

### combine summary percent with centroids

```{r}
( resCentroidreproj = resCentroid %>% 
    rename(resName=ECO_NAME) %>%
    st_transform(., crs = polarProj) %>% 
    dplyr::mutate(x = sf::st_coordinates(.)[,1],
                y = sf::st_coordinates(.)[,2]) %>%
  left_join(., resPtCt, by='resName') 
)


```

## Save 

```{r eval=FALSE, include=FALSE}
st_write(resCentroidreproj, "../outputs/spatialDataCreate/EcozoneResCentroids2024-02-23.gpkg")
```



