---
title: "ERA5 Test"
author: "Anna Talucci"
date: "2024-10-16"
output: html_document
---



# clear environment
```{r}
rm(list=ls())
```

# Overview

Take extracted ERA 5 data from google earth engine...

ERA5 data was extract by year
# Packages

```{r}
library(tidyverse)
library(lubridate)
library(sf)
library(data.table)
```



# Data

## vector of data files
```{r}
f <- list.files(path = "../data/ERA5Test20152016/",
                pattern = "*.csv", full.names = TRUE)
```

```{r}
f
```

## Holloway
```{r}
f2015 <- read.csv(f[1], header = TRUE) 
f2016 <- read.csv(f[2], header = TRUE) 
#f2023 <- read.csv(f[3], header = TRUE) 
```

```{r}
names(f2015)
```




## Process
1. pivot longer so column of temperature and date
2. Group by site_id
3. Select dates after day of thaw measurement
4. Select only rows with temp above 0 (zero)
5. Apply calculation

 

# Functions to clean 

```{r}
selectColDf = function(x)  {
  x %>%
    dplyr::select(EXTENT:year,  contains("mean_2m_air_temperature")) %>%
    mutate(id = row_number()) -> x
  return(x)
}
```

```{r}
cleanDf = function(x)  {
  x %>%
  pivot_longer(
    cols = starts_with("X"),
    names_to = "DateTemp",
    values_to = "TempC",
    values_drop_na = TRUE) %>% 
  separate(DateTemp, c("tempDate", NA)) %>% 
    mutate(across(tempDate, ~ . |> str_extract("\\d+") |> as.character())) %>%
    mutate(tempDate=ymd(tempDate)) %>%
    mutate(TempDoy = yday(tempDate)) -> x
  return(x)
}
```


##  Apply functions to to each year

### Select Column Function

```{r}
(df2015 = f2015 %>% selectColDf() )
(df2016 = f2016 %>% selectColDf() )
#(df2023 = f2023 %>% selectColDf() )
```



### Clean function

Note: the warning is referencing parts of the name being discarded in the separate process. This can be ignored for these chunks of code.

```{r}
( clean2015 = df2015 %>% cleanDf() )
( clean2016 = df2016 %>% cleanDf() )
#( clean2023 = df2023 %>% cleanDf() )
```


# Function to Identify ALT date for prediction

```{r}
idAltDateFun = function(x)  {
  x %>%
  arrange(id, tempDate) %>%
  group_by(id) %>%
  mutate(RollMean = zoo::rollmean(TempC, k = 5, fill = NA)) %>% 
    filter(TempDoy>=200)  %>%
    ungroup() %>%
    filter(RollMean <=0) %>%
    group_by(site, plot, year, month, day) %>% 
    arrange(TempDoy) %>% # sort by date of temp measures
  mutate(TempDoy_diff = TempDoy - lag(TempDoy)) %>%
  filter(TempDoy_diff >= 1) %>%
  summarize(minDate = min(TempDoy),
            meanDate = mean(TempDoy),
            maxDate = max(TempDoy)) %>%
    ungroup() -> x
  return(x)
}
```

## Identify ALT date

```{r}
(rm2015 = clean2015 %>% idAltDateFun())
(rm2016 = clean2016 %>% idAltDateFun())
#(rm2023 = clean2023 %>% idAltDateFun())
```



## Combine Df together

```{r}
combine2015 = merge(clean2015, rm2015[, c('site', 'plot', 'year', 'month', 'day', 'minDate')], by = c('site', 'plot', 'year', 'month', 'day'), all.x=TRUE) %>% mutate(plot=as.character(plot))
combine2016 = merge(clean2016, rm2016[, c('site', 'plot', 'year', 'month', 'day', 'minDate')], by = c('site', 'plot', 'year', 'month', 'day'), all.x=TRUE) %>% mutate(plot=as.character(plot))
#combine2023 = merge(clean2023, rm2023[, c('site', 'plot', 'year', 'month', 'day', 'minDate')], by = c('site', 'plot', 'year', 'month', 'day'), all.x=TRUE) %>% mutate(plot=as.character(plot))
```

```{r}
combine2015
```

# Bind clean 

Combine yearly data frames; rename columns that were truncated by EE. 

```{r}
( combineAll = dplyr::bind_rows(combine2015, combine2016) %>% #, combine2023
  mutate(predDoy1 = minDate-14) )
```


```{r}
names(combineAll)
```

# write to csv

```{r}
write.csv(combineAll,file = "../outputs/era5Clean/ValidationDataHollowayBreenERA5Test.csv", row.names = FALSE)
```



