---
title: "Figure Proportion of area represented"
author: "Anna Talucci"
date: "2024-03-08"
output: html_document
---

# clear environment
```{r}
rm(list=ls())
```


# Overview
Creat over view map with permafrost extent and summary of site data.
Notes:From PCN-Fire-Sysnthesis "Manuscript Map"
[Better colors for Mapping](https://www.esri.com/arcgis-blog/products/js-api-arcgis/mapping/better-colors-for-better-mapping/)
# Packages
```{r}
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(cowplot)
library(ggpubr)
library(ggnewscale)
library(scales)
library(ggrepel)
library(patchwork)
library(ggridges)

```

# Projection
[Some projection info]https://nsidc.org/data/user-resources/help-center/guide-nsidcs-polar-stereographic-projection)
```{r}
polarProj = "+proj=stere +lat_0=90 +lat_ts=70 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +type=crs"
```

# Data

## Predicted measurements

```{r}
datacubePred = read_csv("../data/dataCube/PermafrostFireDatacubeFinal.csv")
```
```{r}
( datacubePred = datacubePred %>% mutate(Continent = ifelse(cntryId %in% c("US", "CA"), "North America", "Asia")))
```
## Resolve Polygons

```{r}
resolve = st_read("../data/spatialData/RESOLVE_Ecoregions_and_Biomes/Biomes_and_Ecoregions_2017.shp", "Biomes_and_Ecoregions_2017")
```

```{r}
resTarget = c( "Arctic foothills tundra", "Beringia lowland tundra",  "Beringia upland tundra", "Chukchi Peninsula tundra", "East Siberian taiga", "Interior Alaska-Yukon lowland taiga", "Interior Yukon-Alaska alpine tundra", "Muskwa-Slave Lake taiga", "Northeast Siberian taiga", "Northern Canadian Shield taiga",      "Northwest Territories taiga", "Yamal-Gydan tundra")
```

```{r}
resolve1 = resolve %>% filter(ECO_NAME %in% resTarget)
```

## World map
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
wrld = st_read("../data/spatialData/world/WB_countries_Admin0_10m.shp", "WB_countries_Admin0_10m")
```

## permafrost

```{r}
permafrost = st_read("../data/spatialData/permafrost/permaice.shp", "permaice")
```

```{r}
head(permafrost)
```

# Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/spatialData/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```



# Filter shapefiles

## Countries

```{r}
target = c("Asia", "Europe", "North America")
```

Filter for all
```{r}
nh  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```


```{r}
nh
```

## Permafrost

```{r}
permafrost1 = permafrost %>% 
  filter(EXTENT %in% c("C", "D", "S")) 
```

# Reproject

```{r}
nh_pp = st_transform(nh, crs = polarProj)

artic_pp = st_transform(arctic, crs = polarProj)
permafrost1_pp = st_transform(permafrost1, crs = polarProj)
resolve1_pp = st_transform(resolve1, crs = polarProj)
resolveAllpp = st_transform(resolve, crs = polarProj)
```

```{r}
nh_pp
```

```{r}
nh_cropped <- st_crop(nh_pp, xmin = -180, xmax = 180,
                                    ymin = 45, ymax = 90)
```

# Plot themes & pallettes

## themes

```{r}
comp_theme = theme_minimal() + theme(legend.position = "none") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 10, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"))
```

```{r}
theme_legdR = theme_minimal() + theme(legend.position = "right") +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 11, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 10, color = "black"),
        axis.text.y = element_text(size = 10, color = "black"))
```

```{r}
hist_theme = theme_minimal() + 
  theme(legend.position = "none",
        panel.grid.major = element_blank(),
        axis.text.x = element_text(size = 4, color = "black", face = "plain", margin = margin(r = 0, l=0, t=0, b=0)),
        axis.text.y = element_text(size = 4, color = "black", face = "plain", margin = margin(r = 0, l=0, t=0, b=0)), 
        axis.title.x = element_text(size = 5, color = "black", face = "plain", hjust = -.01),
        axis.title.y = element_text(size = 5, color = "black", face = "plain"),
        plot.margin=unit(c(0,5,2,3), "mm")) # t,r,b,l
```

## Palettes
[More Palette options for R](https://stackoverflow.com/questions/9563711/r-color-palettes-for-many-data-classes)
```{r}
ecoPalette = c('#ff7f00','#1f78b4',"#00bfa0",'#fb9a99','#e31a1c','#33a02c','#a6cee3',"#dc0ab4",'#b2df8a','#bebada', '#CC6677', '#b15928')
```



```{r}
sort(unique(datacubePred$resName))
```
| Ecozone                               |  Hexcode   |
|:-------------------------------------:|:----------:|
| "Arctic foothills tundra"             | '#ff7f00'  |
| "Beringia lowland tundra"             | '#1f78b4'  |
| "Beringia upland tundra"              | "#00bfa0"  |
| "Chukchi Peninsula tundra"            | '#fb9a99'  |
| "East Siberian taiga"                 | '#e31a1c'  |
| "Interior Alaska-Yukon lowland taiga" | '#33a02c'  | 
| "Interior Yukon-Alaska alpine tundra" | '#a6cee3'  |
| "Muskwa-Slave Lake taiga"             | "#dc0ab4"  |
| "Northeast Siberian taiga"            | '#b2df8a'  |
| "Northern Canadian Shield taiga"      | '#bebada'  |
| "Northwest Territories taiga"         | '#CC6677'  |
| "Yamal-Gydan tundra"                  | '#b15928'  |


```{r}
permafrost_palette = c('#71A6D1', '#99C4E1', '#C0E2F0')
#permafrost_palette2 = c('#88419d', '#8c6bb1','#8c96c6')
#permafrost_palette3 = c('#c994c7','#d4b9da', '#f1eef6') 
#permafrost_palette4 = c('#4b2665', '#8774ab', '#d4b9da')
```

```{r}
brltnd_palette = c('#4a6741', '#3d3021')
```

# Maps

## Zoom Level

```{r}
#### zoom to kamchatka, different projection ####

zoom_to <- c(180, 83)  # ~ center of Kamchatka
zoom_level <- 2.25

# Lambert azimuthal equal-area projection around center of interest
target_crs <- polarProj#sprintf('+proj=laea +lon_0=%f +lat_0=%f', zoom_to[1], zoom_to[2])


C <- 40075016.686   # ~ circumference of Earth in meters
x_span <- C / 2^(zoom_level+.1)
y_span <- C / 2^(zoom_level+.3)   # also sets aspect ratio

zoom_to_xy <- st_transform(st_sfc(st_point(zoom_to), crs = 4326), crs = target_crs)
zoom_to_xy

disp_window <- st_sfc(st_point(st_coordinates(zoom_to_xy - c(x_span / 2, y_span / 2))),
                      st_point(st_coordinates(zoom_to_xy + c(x_span / 2, y_span / 2))),
                      crs = target_crs)
```

# Build Overview map by Ecozone

## with Resolve Ecozones

```{r}
( ecozoneMap = ggplot() +
      geom_sf(data = nh_pp, fill = "#F9F6EE", colour="#F9F6EE") +
    geom_sf(data = resolveAllpp, fill = "#A9AB9D", color= "#F9F6EE") +
    geom_sf(data = resolve1_pp, aes(fill = ECO_NAME), color= "#F9F6EE", alpha=.9) +
 
  geom_sf(data=artic_pp, fill=NA, colour = '#3d3021', lwd=.5, linetype="dashed") +
    scale_fill_manual(values = ecoPalette, name = "Ecozones") +
    #scale_color_manual(values = ecoPalette, name = "Ecozones") +
  
    labs(x="", y="") +

  coord_sf(xlim = st_coordinates(disp_window)[,'X'], ylim = st_coordinates(disp_window)[,'Y']) +
 theme(panel.grid.major = element_line(color = gray(0.5), linetype = "solid", size = 0.3), 
        panel.background = element_rect(fill = "#f0f8ff"),
        plot.margin=unit(c(0,0,0,0), "mm"),
        legend.key=element_blank(),
        legend.position = "none",        
        legend.text=element_text(size=0),
        legend.title=element_text(size=0)) +
 
  guides(fill=guide_legend( title.position = "top", ncol=3,byrow=TRUE))
  
)
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/EcozoneResMap.png", plot = ecozoneMap, units = c("in"), dpi=600, bg = "white" )
```

### Map Legend

```{r}
( resEcoLegendBottom = ggplot() +
      geom_sf(data = nh_pp, fill = "#F9F6EE", colour="#F9F6EE") +
    geom_sf(data = resolveAllpp, fill = "#F9F6EE", color= "#A9AB9D") +
    geom_sf(data = resolve1_pp, aes(fill = ECO_NAME),lwd = 0, alpha=.9) +
 
  geom_sf(data=artic_pp, fill=NA, colour = '#3d3021', lwd=.5, linetype="dashed") +
    scale_fill_manual(values = ecoPalette, name = "Ecozones") +
    #scale_color_manual(values = ecoPalette, name = "Ecozones") +
  
    labs(x="", y="") +

  coord_sf(xlim = st_coordinates(disp_window)[,'X'], ylim = st_coordinates(disp_window)[,'Y']) +
 theme(panel.grid.major = element_line(color = gray(0.5), linetype = "solid", size = 0.3), 
        panel.background = element_rect(fill = "#f0f8ff"),
        plot.margin=unit(c(0,0,0,0), "mm")) + 
  theme(legend.position = "bottom",
         legend.text=element_text(size=8),
        legend.margin = margin(0, 0, 0, 0),
        legend.title=element_text(size=9),
         legend.key=element_blank(),
        legend.key.size = unit(5, 'mm'),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank()) +
  guides(color = guide_legend(title.position = "top", ncol=2,bycol=TRUE, override.aes = list(size = 4)),
         fill = guide_legend(title.position = "top", ncol=2,bycol=TRUE, override.aes = list(size = 4)))
)
```
```{r}
legendBottom = cowplot::get_legend(resEcoLegendBottom)
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/EcozoneLegendBottom.png", plot = legendBottom, dpi = 600,  bg='white')
```
```{r eval=FALSE, include=FALSE}
ggsave("../figures/EcozoneMapAndLegendBottom.png", plot = resEcoLegendBottom, dpi = 600,  bg='white')
```

```{r}
( resEcoLegendRight = ggplot() +
      geom_sf(data = nh_pp, fill = "#F9F6EE", colour="#F9F6EE") +
    geom_sf(data = resolveAllpp, fill = "#F9F6EE", color= "#A9AB9D", lwd = 0.2,) +
    geom_sf(data = resolve1_pp, aes(fill = ECO_NAME), lwd = 0, alpha=.9) +
 
  geom_sf(data=artic_pp, fill=NA, colour = '#3d3021', lwd=.5, linetype="dashed") +
    scale_fill_manual(values = ecoPalette, name = "Ecozones") +
    #scale_color_manual(values = ecoPalette, name = "Ecozones") +
  
    labs(x="", y="") +

  coord_sf(xlim = st_coordinates(disp_window)[,'X'], ylim = st_coordinates(disp_window)[,'Y']) +
 theme(panel.grid.major = element_line(color = gray(0.5), linetype = "solid", size = 0.3), 
        panel.background = element_rect(fill = "#f0f8ff"),
        plot.margin=unit(c(0,0,0,0), "mm")) +  # t,r,b,l 
  theme(legend.position = "right",
         legend.text=element_text(size=8),
        legend.margin = margin(0, 0, 0, 0),
        legend.title=element_text(size=9),
         legend.key=element_blank(),
        legend.key.size = unit(5, 'mm'),
        axis.title.x = element_blank(), 
        axis.title.y = element_blank()) 
)

```

+
  guides(color = guide_legend(title.position = "top", ncol=4,bycol=TRUE, override.aes = list(size = 4)),
         fill = guide_legend(title.position = "top", ncol=2,bycol=TRUE, override.aes = list(size = 4))) 

```{r}
legendRight = cowplot::get_legend(resEcoLegendRight)
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/EcozoneLegendRight.png", plot = resEcoLegendRight, dpi = 600,  bg='white')
```

# Frequency by Ecozone

```{r eval=FALSE, fig.height=6, fig.width=6, include=FALSE}
( histEco = ggplot(datacubePred, aes(x = predDepth, fill = resName)) +
geom_histogram(stat = "count") +
  facet_wrap(~resName, scales = "free", nrow = 4) +
   scale_fill_manual(values = ecoPalette) +
  #scale_y_continuous(expand = expand_scale(mult = c(0, 0.05))) +
  hist_theme +
    theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 5), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))
)
  #geom_rug(aes(predDepth, y = NULL))
```

```{r eval=FALSE, include=FALSE}
ggsave("../figures/HistogramPredDepthEcozone.png", plot = histEco, width = 6, height =6, units = c("in"), dpi=600, bg = "white" )
```

## Joint frequency
| Ecozone                               |  Hexcode   |
|:-------------------------------------:|:----------:|
| "Arctic foothills tundra"             | '#ff7f00'  |
| "Beringia lowland tundra"             | '#1f78b4'  |
| "Beringia upland tundra"              | "#00bfa0"  |
| "Chukchi Peninsula tundra"            | '#fb9a99'  |
| "East Siberian taiga"                 | '#e31a1c'  |
| "Interior Alaska-Yukon lowland taiga" | '#33a02c'  | 
| "Interior Yukon-Alaska alpine tundra" | '#a6cee3'  |
| "Muskwa-Slave Lake taiga"             | "#dc0ab4"  |
| "Northeast Siberian taiga"            | '#b2df8a'  |
| "Northern Canadian Shield taiga"      | '#bebada'  |
| "Northwest Territories taiga"         | '#CC6677'  |
| "Yamal-Gydan tundra"                  | '#b15928'  |

```{r}
head(datacubePred)
datacubePred$distur[datacubePred$distur == "unburned"] <- "Unburned"
datacubePred$distur[datacubePred$distur == "burned"] <- "Burned"
datacubePred$resBiome[datacubePred$resBiome == "Boreal Forests/Taiga"] <- "Boreal"
( northAmer = datacubePred %>% filter(Continent=="North America") )
( asia = datacubePred %>% filter(Continent=="Asia") )
```



```{r}

( plot_na = ggplot(northAmer, aes(predDepth, colour = resName)) +
  geom_freqpoly(binwidth = 10) +
  facet_grid(vars(resBiome), vars(distur), scales = "free") +
   scale_color_manual(values = c('#ff7f00', '#1f78b4', "#00bfa0", '#33a02c','#a6cee3', "#dc0ab4", '#bebada', '#CC6677'), name="Ecozones") +
  comp_theme +
  theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 8), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt() +
  #scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))
)
```

```{r}
( plot_asia =  ggplot(asia, aes(predDepth, colour = resName)) +
  geom_freqpoly(binwidth = 10) +
  facet_grid(vars(resBiome), vars(distur), scales = "free") +
   scale_color_manual(values = c('#fb9a99','#e31a1c', '#b2df8a', '#b15928'), name="Ecozones") +
  comp_theme +
  theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 8), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt() +
  #scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))
)
```

 
```{r eval=FALSE, include=FALSE}
( plot_naBoreal = northAmer %>% filter(resBiome!="Tundra") %>%
ggplot(., aes(predDepth, colour = resName)) +
  geom_freqpoly(binwidth = 10) +
  facet_wrap(~resBiome + distur, scales = "free", ncol = 2) +
   scale_color_manual(values = c('#33a02c', "#dc0ab4", '#bebada', '#CC6677'), name="Ecozones") +
  comp_theme +
  theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 10), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt() +
  #scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))
)
```

```{r eval=FALSE, include=FALSE}
plot_naTundra = northAmer %>% filter(resBiome=="Tundra") %>%
ggplot(., aes(predDepth, colour = resName)) +
  geom_freqpoly(binwidth = 10) +
  facet_wrap(~resBiome + distur, scales = "free", ncol = 2) +
   scale_color_manual(values = c('#ff7f00', '#1f78b4', "#00bfa0", '#a6cee3'), name="Ecozones") +
  comp_theme +
  theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 10), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt() +
  #scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))
```

```{r eval=FALSE, include=FALSE}
( plot_asiaBoreal = asia %>% filter(resBiome!="Tundra") %>%
ggplot(., aes(predDepth, colour = resName)) +
  geom_freqpoly(binwidth = 10) +
  facet_wrap(~resBiome + distur, scales = "free", ncol = 2) +
   scale_color_manual(values = c('#e31a1c', '#b2df8a'), name="Ecozones") +
  theme_bw() +
  theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 10), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt() +
  #scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))
)
```


```{r eval=FALSE, include=FALSE}
plot_asiaTundra = asia %>% filter(resBiome=="Tundra") %>%
ggplot(., aes(predDepth, colour = resName)) +
  geom_freqpoly(binwidth = 10) +
  facet_wrap(~resBiome + distur, scales = "free", ncol = 2) +
   scale_color_manual(values = c('#fb9a99', '#b15928'), name="Ecozones") +
  
  theme_bw() +
  theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 10), 
          panel.spacing = unit(0,'lines')) +
  labs(x='Depth (cm)', y='Count') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_sqrt() +
  #scale_y_continuous(expand=c(0,0)) +
  theme(panel.spacing = unit(.5, "lines"))

```

# Grid

### Grid map with legend Bottom

```{r}
( topRow = cowplot::plot_grid(plot_na, plot_asia, labels=c("A", "B"), ncol=1) )
( bottomRow = cowplot::plot_grid(resEcoLegendBottom, labels=c("C"), ncol=1) )
```




```{r}
( leftSide = cowplot::plot_grid(plot_na, plot_asia, labels=c("A", "B"), ncol=1) )
```

```{r}
( rightSide = cowplot::plot_grid(ecozoneMap, legendBottom, ncol = 1, rel_heights = c(.8, .1), labels = c("C", "")) )
```

```{r}
cowplot::plot_grid(leftSide, ecozoneMap, nrow=1, rel_widths = c(1.1, .9))
```

```{r}
ggdraw(xlim = c(0, 8), ylim = c(0, 4)) +
    draw_plot(leftSide, x = 0, y = 0, width = 4, height = 4) + 
  draw_image("../figures/EcozoneMapAndLegendBottom.png", scale = 1, x = 4.1, y = 1, width = 3, height = 3) 
```

```{r eval=FALSE, fig.height=6, fig.width=6, include=FALSE}
gridEcoHistMap = ggdraw(xlim = c(0, 6), ylim = c(0, 6)) +
    draw_plot(histEco, x = 0, y = 0, width = 6, height = 5) + 
  draw_image("../images/EcozoneResMap.png", scale = 0.8, x = 2, y = -0.3, width = 2, height = 2) +
  draw_image("../images/EcozoneLegendRight.png", scale = 1, x = 4, y = 0, width = 2, height = 2)
```

### Save Image

```{r eval=FALSE, include=FALSE}
ggsave("../figures/EcozoneHistMap.png", plot = gridEcoHistMap, dpi = 600, width = 6, height = 6, bg='white')
```


# EXTRA 


```{r}
( resArea = resolve1_pp %>% dplyr::mutate(area_meters = st_area(resolve1_pp),
                # 1 m2 = 0.0.000247105 acres
                area_acres = area_meters * 0.000247105,
                # 1m2 = 0.0001 hectares
                area_hectares = area_meters * 0.0001) %>%
    dplyr::select(ECO_NAME, area_hectares) %>%
    rename(resName=ECO_NAME) %>%
    st_drop_geometry()
    )
```



theme_set(theme_ridges())

```{r}
datacubePred
max(datacubePred$predDepth)
( datacube1 = datacubePred %>% filter(predDepth<350) )
max(datacube1$predDepth)
```
# Add marginal rug
ggplot(iris, aes(x = Sepal.Length, y = Species)) +
  geom_density_ridges(
    jittered_points = TRUE,
    position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.7,
  )
```{r}
( densityPlot = ggplot(datacube1, aes(x = predDepth, y = resName, fill = resName, height = after_stat(density))) +
  geom_density_ridges(aes(fill = resName),stat = "density", alpha=.75 , scale = 3) +
  scale_fill_manual(values = ecoPalette, name = "Ecozones") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_discrete(expand = expansion(mult = c(0.01, .1))) +
  theme_ridges() +
   theme(legend.position = "none") +
  labs(x= 'Depth (cm)', y="")
)
  
```


  
jittered_points = TRUE,
    position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 3, point_alpha = 1, alpha = 0.7,
  )
  
```{r}
( densityHistogram = ggplot(datacube1, aes(x = predDepth, y = resName, fill = resName, height = after_stat(density))) +
  geom_density_ridges(aes(fill = resName), stat = "binline", bins = 20, scale = 0.95,
    draw_baseline = FALSE, alpha=.75 , scale = 3, position = position_points_jitter(width = 0.05, height = 0),
    point_shape = '|', point_size = 3, point_alpha = 1) +
  scale_fill_manual(values = ecoPalette, name = "Ecozones") +
  scale_x_continuous(expand = c(0, 0)) +
  scale_y_discrete(expand = expansion(mult = c(0.01, .1))) +
  theme_ridges() +
   theme(legend.position = "none") +
  labs(x= 'Depth (cm)', y="")
)
  
```


# Individual Histograms

```{r}
unique(sort(datacube1$resName))
```


```{r}
( histplot1 = datacube1 %>%
    filter(resName=="Arctic coastal tundra") %>%
    ggplot(aes(x = predDepth)) +
geom_histogram(stat = "count", fill = '#a6cee3') +
  
  hist_theme +
    theme(strip.background = element_rect(color="white", fill="white", size=1.5, linetype="solid"),
          strip.text.x = element_text(size = 5),
          panel.spacing = unit(0,'lines')) +
  labs(x='', y='') +
  scale_x_continuous(expand=c(0,0)) +
  scale_y_continuous(expand=c(0,0))
  #xlim(0, 90) +
  #ylim(0,20)
)
  #geom_rug(aes(predDepth, y = NULL))
```

