---
title: "Burned area overview"
author: "Anna Talucci"
date: "2024-10-21"
output: html_document
---


```{r clear environment}
rm(list=ls())
```

# Overview

# Packages
```{r}
library(terra)
library(tidyverse)
library(sf)
library(rnaturalearth)
library(rnaturalearthdata)
library(RColorBrewer)
library(cowplot)
library(ggpubr)
library(ggnewscale)
library(scales)
library(ggrepel)
library(patchwork)


library(tidyterra)
```


library(mapproj)
library(sf)

library(ggspatial)


library(rasterVis)


# Data 







## points
```{r}
pts = st_read("../outputs/pts.gpkg")
```

```{r}
r = rast("../outputs/burnedArea_wgs.tif")
```

```{r}
sprc_r = sprc(r)
```

```{r}
plot(r)
```


# Projection
[Some projection info]https://nsidc.org/data/user-resources/help-center/guide-nsidcs-polar-stereographic-projection)
```{r}
polarProj = "+proj=stere +lat_0=90 +lat_ts=70 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +type=crs"
```
polarProj = "+proj=stere +lat_0=90 +lat_ts=70 +lon_0=-45 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +type=crs"


## reproject

```{r}
burnedArea_pp <- terra::project(burnedArea, polarProj)
pts_pp <- st_transform(pts, polarProj)
```

## World map
https://datacatalog.worldbank.org/dataset/world-bank-official-boundaries

```{r}
wrld = st_read("../data/spatialData/world/WB_countries_Admin0_10m.shp", "WB_countries_Admin0_10m")
```

# Arctic Circle 
Arctic Circle shapefile came from [Natural Earth](https://www.naturalearthdata.com/downloads/110m-physical-vectors/110m-geographic-lines/)

```{r}
circle = st_read("../data/spatialData/ne_110m_geographic_lines/ne_110m_geographic_lines.shp", "ne_110m_geographic_lines") 
```
```{r}
arctic = circle %>% filter(name=="Arctic Circle")
```

# Filter shapefiles

## Countries

```{r}
target = c("Asia", "Europe", "North America")
```

Filter for all
```{r}
nh  = wrld %>% 
  filter(CONTINENT %in% target) %>%
  dplyr::select( OBJECTID:FORMAL_EN, NAME_EN, ISO_A2, CONTINENT:REGION_WB, Shape_Leng:geometry) 
```


```{r}
nh
```

# Reproject

```{r}
nh_pp = st_transform(nh, crs = polarProj)
artic_pp = st_transform(arctic, crs = polarProj)
```

```{r}
nh_pp
```

```{r}
nh_cropped <- st_crop(nh_pp, xmin = -180, xmax = 180,
                                    ymin = 45, ymax = 90)
```

# Palettes
[More Palette options for R](https://stackoverflow.com/questions/9563711/r-color-palettes-for-many-data-classes)
```{r}
permafrost_palette4 = c('#4b2665', '#8774ab', '#d4b9da')
```

# Maps

## Zoom Level

```{r}
#### zoom to kamchatka, different projection ####

zoom_to <- c(180, 83)  # ~ center of Kamchatka
zoom_level <- 2

# Lambert azimuthal equal-area projection around center of interest
target_crs <- polarProj#sprintf('+proj=laea +lon_0=%f +lat_0=%f', zoom_to[1], zoom_to[2])


C <- 40075016.686   # ~ circumference of Earth in meters
x_span <- C / 2^(zoom_level+.1)
y_span <- C / 2^(zoom_level+.5)   # also sets aspect ratio

zoom_to_xy <- st_transform(st_sfc(st_point(zoom_to), crs = 4326), crs = target_crs)
zoom_to_xy

disp_window <- st_sfc(st_point(st_coordinates(zoom_to_xy - c(x_span / 2, y_span / 2))),
                      st_point(st_coordinates(zoom_to_xy + c(x_span / 2, y_span / 2))),
                      crs = target_crs)

```

# Build Overview map by Ecozone

```{r}
burnedArea_pp
```

```{r}
ggplot() +
  layer_spatial(data = r) 
```

```{r}
plot
```

```{r}
( overview_BA_map = ggplot() +
      geom_sf(data = nh, fill = "#A9AB9D", colour="#A9AB9D") +
    geom_sf(data = pts_pp) +
 
  #geom_sf(data=artic_pp, fill=NA, colour = "black", lwd=1, linetype="dashed") +

    labs(x="", y="") +
coord_sf()+
  #coord_sf(xlim = st_coordinates(disp_window)[,'X'], ylim = st_coordinates(disp_window)[,'Y']) +
 theme(panel.grid.major = element_line(color = gray(0.5), linetype = "solid", size = 0.3), 
        panel.background = element_rect(fill = "#f0f8ff"),
        plot.margin=unit(c(0,0,0,0), "mm"),
        legend.key=element_blank(),
        legend.position = "none",        
        legend.text=element_text(size=0),
        legend.title=element_text(size=0)) +
 
  guides(fill=guide_legend( title.position = "top", ncol=3,byrow=TRUE))
  
)
```
