---
title: "Validation Data Clean"
author: "Anna Talucci"
date: "2024-09-19"
output: html_document
---
```{r}
rm(list=ls())
```

# Overview

Clean validation data for running predictive model

# Packages

```{r}
library(tidyverse)
library(sf)
library(lubridate)
library(stringr)
```




# Breen 

## data files

```{r}
breen = read_csv("../data/validationData/validationDataBreen.csv")
```

```{r}
breen
```
```{r}
breen %>% filter(lon >0)
breen %>% filter(plot=="MP1-23-01")
```

## Organize

```{r}
( breen1 = breen %>% 
  dplyr::select(plot, site, lat, lon, thaw_depth_202307_1, resistive_layer_202307__1,  active_layer_depth_202310_1, resistive_layer_202310_1) %>%
    filter(resistive_layer_202310_1 != "none") %>%
  dplyr::select(-resistive_layer_202307__1, -resistive_layer_202310_1) %>%
  pivot_longer(
    cols = c(thaw_depth_202307_1, active_layer_depth_202310_1),
    names_to = "description",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
  mutate(msrType = ifelse(description=="thaw_depth_202307_1", "thaw", "active")) %>%
  mutate(msrDate = ifelse(description=="thaw_depth_202307_1", "2023-07-01", "2023-10-01")) %>%
  mutate(msrDate = as.Date(ymd(msrDate))) %>%
  mutate(predDate = as.Date(ymd("2023-10-01"))) %>% 
  mutate(predDoy = yday(predDate)) %>%
    mutate(msrDate1 = msrDate) %>%
    separate(msrDate1, into=c("year", "month", "day"), sep="\\-") %>%
    mutate(lastNm = "Breen", 
           dateGroup = "z1")  
)
```
```{r}
unique(breen1$fire_scar)
unique(breen1$plot_number)
```



# Holloway

## Data vector of data files Holloway

```{r}
f <- list.files(path = "../data/validationData/holloway",
                pattern = "*.csv", full.names = TRUE)
```

```{r}
f
```

## Read Individual files

```{r}
f1 <- read_csv(f[1], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f2 <- read_csv(f[2], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f3 <- read_csv(f[3], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f4 <- read_csv(f[4], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f5 <- read_csv(f[5], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/") 
f6 <- read_csv(f[6], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f7 <- read_csv(f[7], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f8 <- read_csv(f[8], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f9 <- read_csv(f[9], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/") 
f10 <- read_csv(f[10], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
f11 <- read_csv(f[11], id = "name") %>% mutate(name = str_remove_all(name, ".csv")) %>% separate(name, into=c("folder1", "folder2", "folder3", "folder4", "site"), sep="\\/")
```

### b1 

```{r}
head(f1)
```
```{r}
( f1_msr = f1 %>% 
  dplyr::select(-description_2015_06_17, -description_2015_08_16, -description_2016_05_17, -description_2016_09_01) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
  mutate(msrType = ifelse(date %in% c( "msr_2015_06_17", "msr_2016_05_17"), "thaw","active")) %>%
  mutate(dateGroup = ifelse(date %in% c( "msr_2015_06_17", "msr_2015_08_16"), "a1","a2")) %>%
  mutate(predDate = ifelse(dateGroup %in% c( "a1"), "2015-08-16","2016-09-01")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f1_descriptor = f1 %>% 
  dplyr::select(-msr_2015_06_17, -msr_2015_08_16, -msr_2016_05_17, -msr_2016_09_01) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```
```{r}
( join_b1 = f1_msr %>% right_join(., f1_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### b12 

```{r}
head(f2)
```

```{r}
( f2_msr = f2 %>% 
  dplyr::select(-description_2015_06_06, -description_2015_08_20, -description_2016_05_20, -description_2016_09_15) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
    mutate(msrType = ifelse(date %in% c( "msr_2015_06_06", "msr_2016_05_20"), "thaw","active")) %>%
    mutate(dateGroup = ifelse(date %in% c( "msr_2015_06_06", "msr_2015_08_20"), "b1","b2")) %>%
    mutate(predDate = ifelse(dateGroup %in% c( "b1"), "2015-08-20","2016-09-15")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f2_descriptor = f2 %>% 
  dplyr::select(-msr_2015_06_06, -msr_2015_08_20, -msr_2016_05_20, -msr_2016_09_15) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```
```{r}
( join_b12 = f2_msr %>% right_join(., f2_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### b13 

```{r}
head(f3)
```

```{r}
( f3_msr = f3 %>% 
  dplyr::select(-description_2015_06_11, -description_2015_08_19, -description_2016_06_03, -description_2016_09_15) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
    mutate(msrType = ifelse(date %in% c( "msr_2015_06_11", "msr_2016_06_03"), "thaw","active")) %>%
    mutate(dateGroup = ifelse(date %in% c( "msr_2015_06_11", "msr_2015_08_19"), "c1","c2")) %>%
    mutate(predDate = ifelse(dateGroup %in% c( "c1"), "2015-08-19","2016-09-15")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f3_descriptor = f3 %>% 
  dplyr::select(-msr_2015_06_11, -msr_2015_08_19, -msr_2016_06_03, -msr_2016_09_15) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```

```{r}
( join_b13 = f3_msr %>% right_join(., f3_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### b14 

```{r}
head(f4)
```
```{r}
( f4_msr = f4 %>% 
  dplyr::select(-description_2016_06_06, -description_2016_09_12) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
    mutate(msrType = ifelse(date %in% c( "msr_2016_06_06"), "thaw","active")) %>%
    mutate(dateGroup = "d1") %>%
    mutate(predDate = "2016-09-12") %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f4_descriptor = f4 %>% 
  dplyr::select(-msr_2016_06_06,  -msr_2016_09_12) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```
```{r}
( join_b14 = f4_msr %>% right_join(., f4_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```


### b15 

```{r}
head(f5)
```

```{r}
( f5_msr = f5 %>% 
  dplyr::select(-description_2015_06_18, -description_2015_08_29) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
     mutate(msrType = ifelse(date == "msr_2015_06_18", "thaw","active")) %>%
    mutate(dateGroup = "e1") %>%
    mutate(predDate = "2015-08-29") %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f5_descriptor = f5 %>% 
  dplyr::select(-msr_2015_06_18, -msr_2015_08_29) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```
```{r}
( join_b15 = f5_msr %>% right_join(., f5_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### b16 

```{r}
head(f6)
```

```{r}
( f6_msr = f6 %>% 
  dplyr::select(-description_2015_06_18, -description_2015_08_30) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
     mutate(msrType = ifelse(date == "msr_2015_06_18", "thaw","active")) %>%
    mutate(dateGroup = "e1") %>%
    mutate(predDate = "2015-08-30") %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f6_descriptor = f6 %>% 
  dplyr::select(-msr_2015_06_18, -msr_2015_08_30) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```
```{r}
( join_b16 = f6_msr %>% right_join(., f6_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### b5 

```{r}
head(f7)
```

```{r}
( f7_msr = f7 %>% 
  dplyr::select(-description_2015_06_12, -description_2015_08_18, -description_2016_05_13, -description_2016_09_05) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
  mutate(msrType = ifelse(date %in% c("msr_2015_06_12", "msr_2016_05_13"), "thaw","active")) %>%
    mutate(dateGroup = ifelse(date %in% c( "msr_2015_06_12", "msr_2015_08_18"), "f1","f2")) %>%
    mutate(predDate = ifelse(dateGroup %in% c( "f1"), "2015-08-18","2016-09-05")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f7_descriptor = f7 %>% 
  dplyr::select(-msr_2015_06_12, -msr_2015_08_18, -msr_2016_05_13, -msr_2016_09_05) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```

```{r}
( join_b5 = f7_msr %>% right_join(., f7_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### b8 

```{r}
head(f8)
```

```{r}
( f8_msr = f8 %>% 
  dplyr::select(-description_2015_06_03, -description_2015_08_17, -description_2016_05_14, -description_2016_09_02) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
  mutate(msrType = ifelse(date %in% c("date_2015_06_03", "date_2016_05_14"), "thaw","active")) %>%
    mutate(dateGroup = ifelse(date %in% c( "date_2015_06_03", "date_2015_08_17"), "g1","g2")) %>%
    mutate(predDate = ifelse(dateGroup %in% c( "g1"), "2015-08-17","2016-09-02")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f8_descriptor = f8 %>% 
  dplyr::select(-msr_2015_06_03, -msr_2015_08_17, -msr_2016_05_14, -msr_2016_09_02) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```

```{r}
( join_b8 = f8_msr %>% right_join(., f8_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```


### b9 

```{r}
head(f9)
```


```{r}
( f9_msr = f9 %>% 
  dplyr::select(-description_2015_06_03, -description_2015_08_12, -description_2016_05_11, -description_2016_09_14) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
  mutate(msrType = ifelse(date %in% c("msr_2015_06_03", "msr_2016_05_11"), "thaw","active")) %>%
    mutate(dateGroup = ifelse(date %in% c( "msr_2015_06_03", "msr_2015_08_12"), "h1","h2")) %>%
    mutate(predDate = ifelse(dateGroup %in% c( "h1"), "2015-08-12","2016-09-14")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f9_descriptor = f9 %>% 
  dplyr::select(-msr_2015_06_03, -msr_2015_08_12, -msr_2016_05_11, -msr_2016_09_14) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```

```{r}
( join_b9 = f9_msr %>% right_join(., f9_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### ub2 

```{r}
head(f10)
```

```{r}
( f10_msr = f10 %>% 
  dplyr::select(-description_2016_05_16, -description_2016_09_09) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>% 
    mutate(msrType = ifelse(date %in% c("msr_2016_05_16"), "thaw","active")) %>%
    mutate(dateGroup = "i2") %>%
    mutate(predDate = "2016-09-09") %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f10_descriptor = f10 %>% 
  dplyr::select(-msr_2016_05_16, -msr_2016_09_09) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```
```{r}
( join_ub2 = f10_msr %>% right_join(., f10_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### ub3 

```{r}
head(f11)
```


```{r}
( f11_msr = f11 %>% 
  dplyr::select(-description_2015_05_29, -description_2015_08_11, -description_2016_05_10, -description_2016_05_31, -description_2016_09_16) %>%
  pivot_longer(
    cols = starts_with("msr"),
    names_to = "date",
    values_to = "msrDepth",
    values_drop_na = FALSE) %>%
  mutate(msrType = ifelse(date %in% c("msr_2015_05_29", "msr_2016_05_10", "msr_2016_05_31"), "thaw","active")) %>%
     mutate(dateGroup = ifelse(date %in% c( "msr_2015_05_29", "msr_2015_08_11"), "j1","j2")) %>%
    mutate(predDate = ifelse(dateGroup %in% c( "j1"), "2015-08-11","2016-09-16")) %>%
  separate(date, into=c("description", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select(-description, -x, -folder1, -folder2, -folder3) %>%
    rename(lastNm = folder4)
)
```

```{r}
( f11_descriptor = f11 %>% 
  dplyr::select(-msr_2015_05_29, -msr_2015_08_11, -msr_2016_05_10, -msr_2016_05_31, -msr_2016_09_16) %>%
  pivot_longer(
    cols = starts_with("description"),
    names_to = "date",
    values_to = "description",
    values_drop_na = FALSE) %>%
  separate(date, into=c("date", "year", "month", "day"), sep="\\_") %>%
    separate(site, into=c("x", "site"), sep="\\_") %>%
  mutate(date = make_date(year, month, day)) %>%
  dplyr::select( -year, -month, -day, -folder1, -folder2, -folder3, -folder4, -x)
)
```

```{r}
( join_ub3 = f11_msr %>% right_join(., f11_descriptor, by = c("plot", "site", "lat", "lon", "date")) %>%
    drop_na(msrDepth)
)
```

### Combine data frames

```{r}
holloway = bind_rows(join_b1,  join_b5, join_b8, join_b9, join_b12, join_b13, join_b14, join_b15, join_b16, join_ub2, join_ub3) %>% 
  mutate(predDate = as.Date(ymd(predDate)),
         predDoy = yday(predDate),
         plot = as.character(plot)) %>%
  rename(msrDate = date)
```


```{r}
sort(unique(holloway$description))
sort(unique(holloway$year))
```

```{r}
names(holloway)
```

### Save CSV

```{r}
write_csv(holloway, '../outputs/validationClean/HollowayValidationData.csv')
```

# Combine Breen and Holloway
```{r}
holloway
breen1
```

```{r}
sort(names(holloway))
sort(names(breen1))
```

```{r}
( allData = bind_rows(holloway, breen1) )
```

## Create points shapefile

### Function to make points

```{r}
df_to_sf <- function(x){
  st_as_sf(x, coords = c("lon","lat"), crs = 4326, remove = FALSE)
}
```

### Convert to shapefile 

```{r}
( allData_pts = allData %>% 
    df_to_sf() )
```

# Add ecozones

## Reslove data
```{r}
resolve = st_read("../data/spatialData/RESOLVE_Ecoregions_and_Biomes/Biomes_and_Ecoregions_2017.shp", "Biomes_and_Ecoregions_2017")
```

```{r}
permafrost = st_read("../data/spatialData/permafrost/permaice.shp", "permaice")
```
# Projection
[Some projection info]https://nsidc.org/data/user-resources/help-center/guide-nsidcs-polar-stereographic-projection)
```{r}
polarProj = "+proj=stere +lat_0=90 +lat_ts=70 +lon_0=0 +x_0=0 +y_0=0 +datum=WGS84 +units=m +no_defs +type=crs"
```

## transform

```{r}
allData_pts_pp = st_transform(allData_pts, crs = polarProj)
resolve_pp = st_transform(resolve, crs = polarProj)
permafrost_pp = st_transform(permafrost, crs = polarProj) %>% dplyr::select(EXTENT)
```

## Join pts to ecozones

```{r}
( resTunBor = resolve_pp %>% 
    filter(REALM %in% c("Palearctic", "Nearctic")) %>% 
    dplyr::select(OBJECTID, ECO_NAME, BIOME_NUM, BIOME_NAME, REALM, ECO_ID, geometry) %>% 
    filter(BIOME_NUM %in% c(11, 6)) %>%
    rename(resId = OBJECTID, resName=ECO_NAME, resBiomNm = BIOME_NUM, resBiomeName = BIOME_NAME, resRealm = REALM,  resEcoId = ECO_ID) %>%
    dplyr::select(resName, resBiomeName)
)
```

```{r}
resAllData = st_join(allData_pts_pp, resTunBor) 
```

```{r}
resAllData
```

```{r}
resPermaAllData = st_join(resAllData, permafrost_pp) 
```


```{r}
resPermaAllData
```

```{r}
sort(unique(resPermaAllData$year))
sort(unique(resPermaAllData$lastNm))
```

### write to shapefile

```{r}
st_write(resPermaAllData, "../outputs/validationClean/HollowayBreenValidationShapefile.shp", driver="ESRI Shapefile")
```

