---
title: "validation quantify uncertainty"
author: "Anna Talucci"
date: "2024-09-20"
output: html_document
---

# clear environment

```{r}
rm(list=ls())
```

# Overview

validation quantify uncertainty


# Packages

```{r}
library(tidyverse)
library(ggpubr)
library(ggnewscale)
library(ggthemes)
library(ggpmisc)
library(cowplot)
library(Metrics) 
library(sf)
library(scales)
```
# Plot themes

```{r}
comp_theme = theme_bw() +  
  theme(panel.grid.major = element_blank()) +
    theme(axis.title.y = element_text(size = 10, hjust = 0.5, vjust = 1.1),
          axis.title.x = element_text(size = 10, hjust = 0.5, vjust = 1.1),
        axis.text.x = element_text(size = 9, color = "black"),
        axis.text.y = element_text(size = 9, color = "black"))
```


# Data

```{r}
data = read_csv("../outputs/validationPredict/validationPredictHollowayBreen.csv")
```


```{r}
data
```
```{r}
unique(data$plot)
```

```{r}
unique(data$site)
```

```{r}
data$site[data$site == "Delome River"] <- "DR"
data$site[data$site == "Garfield Creek"] <- "GC"
data$site[data$site == "Mingvk Lake"] <- "ML"
data$site[data$site == "Milepost 85"] <- "MP85"
data$site[data$site == "Milepost 86"] <- "MP86"
data$site[data$site == "Unburned; Mile 80"] <- "UbMp80"
```

```{r}
unique(data$site)
```

# Split by Early and late

```{r}
( early = data %>% 
    filter(msrType=="thaw") %>%
    dplyr::select(-A_sum, -A, -B_sum, -B, -C, -resName, -resBmNm))
( late = data %>% 
    filter(msrType=="active") %>% 
    dplyr::select(site:year, msrDpth, dateGrp, resName, resBmNm) %>%
    rename(msrDepthLate = msrDpth))
```

"b1"     "b12"    "b13"    "b15"    "b16"    "b5"     "b8"     "b9"     "UB3"    "b14"    "UB2"   
[12] "DR"     "GC"     "MP85"   "MP86"   "ML"     "UbMp80"

# Validation Data



```{r}
( valData = early %>% 
    full_join(., late, by=c("site", "plot", "dateGrp", "year")) %>%
    mutate(disturbance = ifelse(site %in% c("UB2", "UB3", "UbMp80"), "unburned", "burned")) %>%
    mutate(residualError = msrDepthLate - predDepth) %>% 
    mutate(relativeError = (msrDepthLate - predDepth) / msrDepthLate * 100) %>% 
    mutate(bias1 = predDepth-msrDepthLate) %>%
    mutate(rmseTop = (predDepth-msrDepthLate)^2) %>%
    drop_na(msrDepthLate) %>% 
    drop_na(predDepth) 
)
```

```{r}
sum(valData$bias1)/651
```

```{r}
names(valData)
```


### Summarize
```{r}
valData %>% 
  group_by(resBmNm, disturbance, lastNm) %>%
  summarise(meanResidualError = mean(residualError),
            meanPercentError = mean(relativeError),
            biasSum = sum(bias1),
            n=n(),
            correlation = cor(msrDepthLate, predDepth), 
            rmseSum = sum(rmseTop)) %>%  
  mutate(bias = biasSum/n,
         rmse = sqrt(rmseSum/n)) %>%
  drop_na(meanResidualError) %>%
  dplyr::select(resBmNm:lastNm, bias, rmse, correlation, n)

```

```{r}
unburnTundra = valData %>% filter(disturbance == "unburned") %>% filter(resBmNm == "Tundra")
burnTundra = valData %>% filter(disturbance == "burned") %>% filter(resBmNm == "Tundra")
unburnBoreal = valData %>% filter(disturbance == "unburned") %>% filter(resBmNm == "Boreal Forests/Taiga")
( burnBoreal = valData %>% filter(disturbance == "burned") %>% filter(resBmNm == "Boreal Forests/Taiga") %>% drop_na(predDepth) )
```
```{r}
model_unburnTundra = lm(predDepth ~ msrDepthLate, data = unburnTundra) 
model_burnTundra = lm(predDepth ~ msrDepthLate, data = burnTundra)
model_unburnBoreal = lm(predDepth ~ msrDepthLate, data = unburnBoreal) 
model_burnBoreal = lm(predDepth ~ msrDepthLate, data = burnBoreal)
```

```{r}
summary(model_unburnTundra)
summary(model_burnTundra)
summary(model_unburnBoreal)
summary(model_burnBoreal)
```


# Plots

## unburned
color="#3d5a80"
```{r}
(unburned = valData %>% filter(disturbance=="unburned") %>% drop_na(msrDepthLate) %>% drop_na(predDepth) )
```
```{r}
max(unburned$predDepth)
max(unburned$msrDepthLate)
min(unburned$predDepth)
min(unburned$msrDepthLate)
```

```{r}
( observPredPlotUnburned = ggplot(unburned, aes(x=msrDepthLate, y=predDepth)) +
  geom_abline (slope=1, intercept = 0, linetype = "solid", color="#f7aa58")+
    geom_point(size =1, shape=1, aes(color=resBmNm)) +
    scale_color_manual(values=c('#59a89c', '#a559aa'), name="Biome", labels=c("Boreal", "Tundra")) +
  #stat_poly_eq() +
  #stat_poly_line() +
    xlim(29, 170) + ylim(29, 170) +
 comp_theme +
   theme(legend.position = "none") + 
   labs(x= "Observed active layer thickness (cm)", y="Estimated active\nlayer thickness (cm)", title="Unburned") +
   theme(title = element_text(size = 10), 
         axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"))
)
```

## Burned
```{r}
(burned = valData %>% filter(disturbance=="burned") %>% drop_na(msrDepthLate) %>% drop_na(predDepth) )
```
```{r}
max(burned$predDepth)
max(burned$msrDepthLate)
min(burned$predDepth)
min(burned$msrDepthLate)
```
```{r}
( observPredPlotBurned = ggplot(burned, aes(x=msrDepthLate, y=predDepth)) +
  geom_abline (slope=1, intercept = 0, linetype = "solid", color="#f7aa58")+
   geom_point(size = 1, shape=1, aes(color=resBmNm)) +
    scale_color_manual(values=c('#59a89c', '#a559aa'), name="Biome", labels=c("Boreal", "Tundra")) +
  #stat_poly_eq() +
  #stat_poly_line() +
    xlim(25, 212) + ylim(25, 212) +
 comp_theme +
   theme(legend.position = "none") + 
   labs(x= "Observed active layer thickness (cm)", y="Estimated active\nlayer thickness (cm)", title="Burned") +
   theme(title = element_text(size = 10), 
         axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 8, color = "black"),
        axis.text.y = element_text(size = 8, color = "black"))
)
```

## All data plot


```{r}
( residualErrorPlot = ggplot(valData, aes(x=site, y=bias1)) +
  geom_hline(yintercept=0, color="gray", size = 3, alpha = .5) +
    geom_boxplot( linewidth = .3, outlier.shape = NA, aes(color=resBmNm)) + #, size = 3, shape = 21
  geom_jitter( size = 1, shape = 21, aes(color=resBmNm)) +
  #geom_point(size =1, shape=1, aes(color=resBmNm)) +
    scale_color_manual(values=c('#59a89c', '#a559aa'), name="Biome", labels=c("Boreal", "Tundra")) +
    stat_summary(fun=mean, geom="point", shape=23, size=2, color="#082a54") +
 comp_theme +
   theme(legend.position = c(.5, .1)) +
   guides(color=guide_legend(ncol=2, title.position = "left")) +
   labs(x= "Plot", y="Residual Error (cm)") +
   theme(title = element_text(size = 10), 
         axis.title.y = element_text(size = 9),
        axis.text.x = element_text(size = 8, color = "black", angle = 90, vjust = 0.5, hjust=1),
        axis.text.y = element_text(size = 8, color = "black"))+
  annotate(
    'text',
    x = 15.8,
    y = 80,
    label = 'Overestimate',
    fontface = 'plain', 
    size = 3,
    angle= 90,
    color = "gray"
  )  +
  annotate(
    'curve',
    x = 16.3, # Play around with the coordinates until you're satisfied
    y = 20,
    yend = 120,
    xend = 16.3,
    linewidth = .8,
    curvature = 0,
    color="gray",
    arrow = arrow(length = unit(0.4, 'cm'))
  ) +
  annotate(
    'text',
    x = 15.8,
    y = -80,
    label = 'Underestimate',
    fontface = 'plain', 
    size = 3,
    angle= 90,
    color = "gray"
  )  +
  annotate(
    'curve',
    x = 16.3, # Play around with the coordinates until you're satisfied
    y = -20,
    yend = -120,
    xend = 16.3,
    linewidth = .8,
    curvature = 0,
    color="gray",
    arrow = arrow(length = unit(0.4, 'cm'))
  )
)
```


# Combine plots


```{r}
( top = cowplot::plot_grid(observPredPlotUnburned, observPredPlotBurned, ncol=2, labels = c("A", "B"))
)

( bottom = cowplot::plot_grid(residualErrorPlot, ncol=1, labels = "C")
)

( combineTopBottom = cowplot::plot_grid(top, bottom, ncol=1) )
```


```{r eval=FALSE, include=FALSE}
ggsave("../figures/ValidationPlotsBurnUnburn.png", plot = combineTopBottom, dpi = 600, width = 6, height = 6, bg='white')
```



# Linear Model Cross Validation

## All Data lm with cross validation
 [medium article](https://medium.com/@josef.waples/k-fold-cross-validation-for-linear-regression-in-r-using-mtcars-2e9cf8b6a289)
 
```{r}
model = lm(predDepth ~ msrDepthLate, data = dfVal) 
```

```{r}
summary(model)
```

```{r}
# Get predicted values from the model
predicted <- predict(model)

# Calculate residuals
residuals <- dfVal$predDepth - predicted

# Calculate RMSE
rmse <- sqrt(mean(residuals^2))

# Print RMSE
print(paste("RMSE:", rmse))
```
```{r}
dfVal %>%
  mutate(fold_number = rep(c("Fold1", "Fold2", "Fold3", "Fold4"), length.out = n())) -> dfVal

# Create separate dataframes for each fold
everything_except_fold1 <- filter(dfVal, fold_number != "Fold1")
everything_except_fold2 <- filter(dfVal, fold_number != "Fold2")
everything_except_fold3 <- filter(dfVal, fold_number != "Fold3")
everything_except_fold4 <- filter(dfVal, fold_number != "Fold4")
```

```{r}
model_fold_2_3_4 <- lm(predDepth ~ msrDepthLate, data = everything_except_fold1)
model_fold_3_4_1 <- lm(predDepth ~ msrDepthLate, data = everything_except_fold2)
model_fold_4_1_2 <- lm(predDepth ~ msrDepthLate, data = everything_except_fold3)
model_fold_1_2_3 <- lm(predDepth ~ msrDepthLate, data = everything_except_fold4)
```

```{r}
fold1 <- filter(dfVal, fold_number == "Fold1")
fold2 <- filter(dfVal, fold_number == "Fold2")
fold3 <- filter(dfVal, fold_number == "Fold3")
fold4 <- filter(dfVal, fold_number == "Fold4")
```

```{r}
fold1
```

```{r}
# Predict using model_fold1 on fold 2, 3, and 4
predictions_fold1 <- predict(model_fold_2_3_4, newdata = fold1)
predictions_fold2 <- predict(model_fold_3_4_1, newdata = fold2)
predictions_fold3 <- predict(model_fold_4_1_2, newdata = fold3)
predictions_fold4 <- predict(model_fold_1_2_3, newdata = fold4)
```

```{r}
fold1
```
```{r}
# Calculate RMSE for each fold
rmse_fold1 <- sqrt(mean((fold1$predDepth - predictions_fold1)^2))
rmse_fold2 <- sqrt(mean((fold2$predDepth - predictions_fold2)^2))
rmse_fold3 <- sqrt(mean((fold3$predDepth - predictions_fold3)^2))
rmse_fold4 <- sqrt(mean((fold4$predDepth - predictions_fold4)^2))

# Print RMSE for each fold
print(paste("RMSE for Fold 1:", rmse_fold1))
print(paste("RMSE for Fold 2:", rmse_fold2))
print(paste("RMSE for Fold 3:", rmse_fold3))
print(paste("RMSE for Fold 4:", rmse_fold4))

(rmse_fold1 + rmse_fold2 + rmse_fold3 + rmse_fold4) / 4
```
predDepth ~ msrDepthLate + disturbance
```{r}
one <- ggplot(everything_except_fold1, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_fold_2_3_4$coefficients[1], slope = model_fold_2_3_4$coefficients[2], color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'folds 2, 3, 4') +
  comp_theme 

two <- ggplot(everything_except_fold2, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_fold_3_4_1$coefficients[1], slope = model_fold_3_4_1$coefficients[2], color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'folds 1, 3, 4') +
  comp_theme

three <- ggplot(everything_except_fold3, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_fold_4_1_2$coefficients[1], slope = model_fold_4_1_2$coefficients[2], color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'folds 1, 2, 4')+
  comp_theme 

four <- ggplot(everything_except_fold4, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_fold_1_2_3$coefficients[1], slope = model_fold_1_2_3$coefficients[2], color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'folds 1, 2, 3') +
  comp_theme 

library(patchwork)

one + two + three + four
```

```{r}
df1 <- data.frame(fold1$predDepth, predictions_fold1)
df1
one <- ggplot(df1, aes(y = fold1.predDepth, x = predictions_fold1)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'prediction vs actual - folds 1, 2, 3') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme 

df2 <- data.frame(fold2$predDepth, predictions_fold2)

two <- ggplot(df2, aes(y = fold2.predDepth, x = predictions_fold2)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'prediction vs actual - folds 1, 3, 4') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

df3 <- data.frame(fold3$predDepth, predictions_fold3)

three <- ggplot(df3, aes(y = fold3.predDepth, x = predictions_fold3)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'prediction vs actual - folds 1, 2, 4') +
  #xlim(12, 20) + ylim(12, 20) + 
  xlab("predictions") + ylab("actual") +
 comp_theme


df4 <- data.frame(fold4$predDepth, predictions_fold4)

four <- ggplot(df4, aes(y = fold4.predDepth, x = predictions_fold4)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("All data") + labs(subtitle = 'prediction vs actual - folds 1, 2, 3') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

library(patchwork)

one + two + three + four
```

## Burned lm with cross validation
 [medium article](https://medium.com/@josef.waples/k-fold-cross-validation-for-linear-regression-in-r-using-mtcars-2e9cf8b6a289)
 
```{r}
model_burned = lm(predDepth ~ msrDepthLate, data = burned) 
```

```{r}
summary(model_burned)
```

```{r}
# Get predicted values from the model
predicted <- predict(model_burned)

# Calculate residuals
residuals <- burned$predDepth - predicted

# Calculate RMSE
rmse <- sqrt(mean(residuals^2))

# Print RMSE
print(paste("RMSE:", rmse))
```
```{r}
burned %>%
  mutate(fold_number = rep(c("Fold1", "Fold2", "Fold3", "Fold4"), length.out = n())) -> burned

# Create separate dataframes for each fold
burned_everything_except_fold1 <- filter(burned, fold_number != "Fold1")
burned_everything_except_fold2 <- filter(burned, fold_number != "Fold2")
burned_everything_except_fold3 <- filter(burned, fold_number != "Fold3")
burned_everything_except_fold4 <- filter(burned, fold_number != "Fold4")
```

```{r}
model_burned_fold_2_3_4 <- lm(predDepth ~ msrDepthLate, data = burned_everything_except_fold1)
model_burned_fold_3_4_1 <- lm(predDepth ~ msrDepthLate, data = burned_everything_except_fold2)
model_burned_fold_4_1_2 <- lm(predDepth ~ msrDepthLate, data = burned_everything_except_fold3)
model_burned_fold_1_2_3 <- lm(predDepth ~ msrDepthLate, data = burned_everything_except_fold4)
```

```{r}
burned_fold1 <- filter(burned, fold_number == "Fold1")
burned_fold2 <- filter(burned, fold_number == "Fold2")
burned_fold3 <- filter(burned, fold_number == "Fold3")
burned_fold4 <- filter(burned, fold_number == "Fold4")
```


```{r}
# Predict using model_fold1 on fold 2, 3, and 4
burned_predictions_fold1 <- predict(model_burned_fold_2_3_4, newdata = burned_fold1)
burned_predictions_fold2 <- predict(model_burned_fold_3_4_1, newdata = burned_fold2)
burned_predictions_fold3 <- predict(model_burned_fold_4_1_2, newdata = burned_fold3)
burned_predictions_fold4 <- predict(model_burned_fold_1_2_3, newdata = burned_fold4)
```


```{r}
# Calculate RMSE for each fold
burned_rmse_fold1 <- sqrt(mean((burned_fold1$predDepth - burned_predictions_fold1)^2))
burned_rmse_fold2 <- sqrt(mean((burned_fold2$predDepth - burned_predictions_fold2)^2))
burned_rmse_fold3 <- sqrt(mean((burned_fold3$predDepth - burned_predictions_fold3)^2))
burned_rmse_fold4 <- sqrt(mean((burned_fold4$predDepth - burned_predictions_fold4)^2))

# Print RMSE for each fold
print(paste("RMSE for Fold 1:", burned_rmse_fold1))
print(paste("RMSE for Fold 2:", burned_rmse_fold2))
print(paste("RMSE for Fold 3:", burned_rmse_fold3))
print(paste("RMSE for Fold 4:", burned_rmse_fold4))

(burned_rmse_fold1 + burned_rmse_fold2 + burned_rmse_fold3 + burned_rmse_fold4) / 4
```
predDepth ~ msrDepthLate + disturbance
```{r}
burned_one <- ggplot(everything_except_fold1, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_burned_fold_2_3_4$coefficients[1], slope = model_burned_fold_2_3_4$coefficients[2], color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'folds 2, 3, 4') +
 comp_theme

burned_two <- ggplot(everything_except_fold2, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_burned_fold_3_4_1$coefficients[1], slope = model_burned_fold_3_4_1$coefficients[2], color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'folds 1, 3, 4') +
 comp_theme

burned_three <- ggplot(everything_except_fold3, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_burned_fold_4_1_2$coefficients[1], slope = model_burned_fold_4_1_2$coefficients[2], color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'folds 1, 2, 4') +
 comp_theme

burned_four <- ggplot(everything_except_fold4, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_burned_fold_1_2_3$coefficients[1], slope = model_burned_fold_1_2_3$coefficients[2], color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'folds 1, 2, 3') +
 comp_theme

library(patchwork)

burned_one + burned_two + burned_three + burned_four
```

```{r}
burned_df1 <- data.frame(burned_fold1$predDepth, burned_predictions_fold1)
burned_df1
burned_one <- ggplot(burned_df1, aes(y = burned_fold1.predDepth, x = burned_predictions_fold1)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'prediction vs actual - folds 1, 2, 3') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

burned_df2 <- data.frame(burned_fold2$predDepth, burned_predictions_fold2)

burned_two <- ggplot(burned_df2, aes(y = burned_fold2.predDepth, x = burned_predictions_fold2)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'prediction vs actual - folds 1, 3, 4') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

burned_df3 <- data.frame(burned_fold3$predDepth, burned_predictions_fold3)

burned_three <- ggplot(burned_df3, aes(y = burned_fold3.predDepth, x = burned_predictions_fold3)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'prediction vs actual - folds 1, 2, 4') +
  #xlim(12, 20) + ylim(12, 20) + 
  xlab("predictions") + ylab("actual") +
 comp_theme


burned_df4 <- data.frame(burned_fold4$predDepth, burned_predictions_fold4)

burned_four <- ggplot(burned_df4, aes(y = burned_fold4.predDepth, x = burned_predictions_fold4)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Burned") + labs(subtitle = 'prediction vs actual - folds 1, 2, 3') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual")+
 comp_theme

library(patchwork)

burned_one + burned_two + burned_three + burned_four
```


## Unburned lm with cross validation
 [medium article](https://medium.com/@josef.waples/k-fold-cross-validation-for-linear-regression-in-r-using-mtcars-2e9cf8b6a289)
 
```{r}
model_unburned = lm(predDepth ~ msrDepthLate, data = unburned) 
```

```{r}
summary(model_unburned)
```

```{r}
# Get predicted values from the model
predicted <- predict(model_unburned)

# Calculate residuals
residuals <- unburned$predDepth - predicted

# Calculate RMSE
rmse <- sqrt(mean(residuals^2))

# Print RMSE
print(paste("RMSE:", rmse))
```
```{r}
unburned %>%
  mutate(fold_number = rep(c("Fold1", "Fold2", "Fold3", "Fold4"), length.out = n())) -> unburned

# Create separate dataframes for each fold
unburned_everything_except_fold1 <- filter(unburned, fold_number != "Fold1")
unburned_everything_except_fold2 <- filter(unburned, fold_number != "Fold2")
unburned_everything_except_fold3 <- filter(unburned, fold_number != "Fold3")
unburned_everything_except_fold4 <- filter(unburned, fold_number != "Fold4")
```

```{r}
model_unburned_fold_2_3_4 <- lm(predDepth ~ msrDepthLate, data = unburned_everything_except_fold1)
model_unburned_fold_3_4_1 <- lm(predDepth ~ msrDepthLate, data = unburned_everything_except_fold2)
model_unburned_fold_4_1_2 <- lm(predDepth ~ msrDepthLate, data = unburned_everything_except_fold3)
model_unburned_fold_1_2_3 <- lm(predDepth ~ msrDepthLate, data = unburned_everything_except_fold4)
```

```{r}
unburned_fold1 <- filter(unburned, fold_number == "Fold1")
unburned_fold2 <- filter(unburned, fold_number == "Fold2")
unburned_fold3 <- filter(unburned, fold_number == "Fold3")
unburned_fold4 <- filter(unburned, fold_number == "Fold4")
```


```{r}
# Predict using model_fold1 on fold 2, 3, and 4
unburned_predictions_fold1 <- predict(model_unburned_fold_2_3_4, newdata = unburned_fold1)
unburned_predictions_fold2 <- predict(model_unburned_fold_3_4_1, newdata = unburned_fold2)
unburned_predictions_fold3 <- predict(model_unburned_fold_4_1_2, newdata = unburned_fold3)
unburned_predictions_fold4 <- predict(model_unburned_fold_1_2_3, newdata = unburned_fold4)
```


```{r}
# Calculate RMSE for each fold
unburned_rmse_fold1 <- sqrt(mean((unburned_fold1$predDepth - unburned_predictions_fold1)^2))
unburned_rmse_fold2 <- sqrt(mean((unburned_fold2$predDepth - unburned_predictions_fold2)^2))
unburned_rmse_fold3 <- sqrt(mean((unburned_fold3$predDepth - unburned_predictions_fold3)^2))
unburned_rmse_fold4 <- sqrt(mean((unburned_fold4$predDepth - unburned_predictions_fold4)^2))

# Print RMSE for each fold
print(paste("RMSE for Fold 1:", unburned_rmse_fold1))
print(paste("RMSE for Fold 2:", unburned_rmse_fold2))
print(paste("RMSE for Fold 3:", unburned_rmse_fold3))
print(paste("RMSE for Fold 4:", unburned_rmse_fold4))

(unburned_rmse_fold1 + unburned_rmse_fold2 + unburned_rmse_fold3 + unburned_rmse_fold4) / 4
```
predDepth ~ msrDepthLate + disturbance
```{r}
unburned_one <- ggplot(everything_except_fold1, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_unburned_fold_2_3_4$coefficients[1], slope = model_unburned_fold_2_3_4$coefficients[2], color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'folds 2, 3, 4') +
 comp_theme

unburned_two <- ggplot(everything_except_fold2, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_unburned_fold_3_4_1$coefficients[1], slope = model_unburned_fold_3_4_1$coefficients[2], color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'folds 1, 3, 4') +
 comp_theme

unburned_three <- ggplot(everything_except_fold3, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_unburned_fold_4_1_2$coefficients[1], slope = model_unburned_fold_4_1_2$coefficients[2], color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'folds 1, 2, 4') +
 comp_theme

unburned_four <- ggplot(everything_except_fold4, aes(x = msrDepthLate, y = predDepth)) +
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = model_unburned_fold_1_2_3$coefficients[1], slope = model_unburned_fold_1_2_3$coefficients[2], color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'folds 1, 2, 3') +
 comp_theme

library(patchwork)

unburned_one + unburned_two + unburned_three + unburned_four
```

```{r}
unburned_df1 <- data.frame(unburned_fold1$predDepth, unburned_predictions_fold1)
unburned_df1
unburned_one <- ggplot(unburned_df1, aes(y = unburned_fold1.predDepth, x = unburned_predictions_fold1)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'prediction vs actual - folds 1, 2, 3') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

unburned_df2 <- data.frame(unburned_fold2$predDepth, unburned_predictions_fold2)

unburned_two <- ggplot(unburned_df2, aes(y = unburned_fold2.predDepth, x = unburned_predictions_fold2)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'prediction vs actual - folds 1, 3, 4') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

unburned_df3 <- data.frame(unburned_fold3$predDepth, unburned_predictions_fold3)

unburned_three <- ggplot(unburned_df3, aes(y = unburned_fold3.predDepth, x = unburned_predictions_fold3)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'prediction vs actual - folds 1, 2, 4') +
  #xlim(12, 20) + ylim(12, 20) + 
  xlab("predictions") + ylab("actual") +
 comp_theme


unburned_df4 <- data.frame(unburned_fold4$predDepth, unburned_predictions_fold4)

unburned_four <- ggplot(unburned_df4, aes(y = unburned_fold4.predDepth, x = unburned_predictions_fold4)) + 
  geom_point(size = 1, shape=1, color="#3d5a80")  + 
  geom_abline(intercept = 0, slope = 1, color = "#f7aa58") +
  ggtitle("Unburned") + labs(subtitle = 'prediction vs actual - folds 1, 2, 3') +
  #xlim(12, 20) + ylim(12, 20) +
  xlab("predictions") + ylab("actual") +
 comp_theme

library(patchwork)

unburned_one + unburned_two + unburned_three + unburned_four
```


