---
title: "Validation ERA5 Test estimate ALT"
author: "Anna Talucci"
date: "2024-10-16"
output: html_document
---



# clear environment

```{r}
rm(list=ls())
```

# Overview

Take field measure active layer depth and predict maximum depth based on air temperature.

# Packages

```{r}
library(tidyverse)
library(lubridate)
library(sf)
```

# Data

```{r}
data = read_csv("../outputs/era5Clean/ValidationDataHollowayBreenERA5Test.csv")
```


# View data

```{r}
glimpse(data)

```
# Date column

```{r}
( data = data %>% 
  mutate(date = make_date(year, month, day)) %>% 
  mutate(msrDoy = yday(date)) 
)

```

# Functions to standarize

Formula Parts 
A. Take the square root of the Sum of the total degrees above zero for dates prior to thaw depth measure
B. Take the square root of the Sum of the total degrees above zero for dates prior to active layer thickness date ()

C. Divide B by A
F. Multiply thaw depth measure by C

```{r}
calc_A = function(x) {
  x %>% 
    group_by(year, id, site, msrDoy) %>%
    filter(TempDoy < msrDoy) %>%
  filter(TempC > 0) %>%
    arrange(TempDoy) %>%
  summarize( 
  A_sum = sum(TempC),
  A = sqrt(A_sum)) -> x
  return(x)
}

```


```{r}

calc_B = function(x) {
  x %>% 
    group_by(year, id, site, msrDoy) %>%
    filter(TempDoy < predDoy) %>%
  filter(TempC > 0) %>%
    arrange(TempDoy) %>%
  summarize( 
  B_sum = sum(TempC),
  B = sqrt(B_sum)) -> x
  return(x)
 }
```

### Calculate A & B

```{r}
( calc_A_data = calc_A(data) )
```

```{r}
( calc_B_data = calc_B(data) )
```


### Filter original data 

```{r}
( orgData = data %>% 
  group_by(year, id, site) %>%
  filter(TempDoy == predDoy)
)
  
```




### Join Calculations with Orginial Data

```{r}
( dataCombine = orgData %>% 
    full_join(y=calc_A_data, by=c("year", "id", 'site', 'msrDoy')) %>%
    full_join(y=calc_B_data, by=c("year", "id", 'site', 'msrDoy')) %>%
    mutate(A_sum = ifelse(is.na(A_sum), 0, A_sum),
           A =ifelse(is.na(A), 0, A)) %>%
    mutate(C = B/A) %>%
    mutate(predDepth = round((msrDpth*C), 0)) 
    )
```



# Remove outliers, na, and INF

```{r}
dataCombine %>% filter_at(vars(predDepth), all_vars(is.infinite(.)))
dataCombine %>% filter(if_any(predDepth, is.infinite))
dataCombine %>% filter(if_any(predDepth, is.na))
```

### Write to csv

```{r}
write.csv(dataCombine, file = "../outputs/validationPredict/validationPredictHollowayBreenTest.csv", row.names=FALSE)
```

